### 2018-07-06 paper/6-engineering.tex
Refer to examples of polymorphism in the framework

\Shake users have remarked that polymorphism provides a much easier expression
of concepts, e.g.~\cite{hadrian}, but it is not essential and thus not necessary
to model.

>>>>

\Shake users have remarked that polymorphism provides a much easier expression
of concepts, e.g.~\cite{hadrian}, but it is not essential and we therefore do
not model it in this paper\footnote{See modules \cmd{Build.Multi} and
\cmd{Build.Task.Typed} in our framework for models of multiple-output and
polymorphic tasks.}.
